Handling String-Number Conversion in String Constraint Solving

### 2019-11-11 evaluation.tex
attempt to improve the experimental section, part 1

In this section, we compare our implementation z3-Trau with other SMT tools cvc4, z3, and z3-str3 as evauation. To show the general performance of z3-Trau, we compare z3-Trau with other string solvers on selected string benchmarks: PyEx is a benchmark obtained from symbolic execution of Python code[]; APLAS is a benchmark involving looping word equations[]; 
LeetCode is obtiained from concolic testing LeetCode solutions written in Python code; StringFuzz is a benchmark of instance SMT-lib string problems generated by StringFuzz generator tool[]; cvc4\textsubscript{pred} and cvc4\textsubscript{term} are benchmarks provided by the cvc4 development team[]. Table~\ref{table:base_benchmark} shows the result of the comparison. The experiments are conducted with machines of the following specifications: 4-core CPU, 8GB RAM, Ubuntu 18.4-LVM OS. We set the timeout is to 10 seconds. Because the amount of problems is very large, we ran these experiments separately on several machines with the same specification on a computer cluster. The results are either sat, unsat, timeout, or $\times$. In case $\times$, the result may be unknown, error, or exception.

>>>>

We have implemented the proposed approach in a prototype tool \textsf{z3-Trau} as a part of the Z3 theorem prover. This approach allows us to efficiently solve not only formulae over string constraints, but also combine string constraints with constraints over other theories that Z3 supports. Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to parse input formulae.

We compare \textsf{z3-Trau} with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{z3str3}~\cite{zheng2013z3}, Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{parosh2019chain}. We do not compare with Sloth \cite{sloth} since it does not support length constraints. We present data on two benchmark groups (see Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}) that demonstrate two points. First, only our tool can efficiently solve formulae that contain string-number and number-string conversion constraints and which can be a combination of constraints over multiple theories. Second, we show that our tool is competitive on well-known benchmarks that can be effectively handled by other existing solvers. All experiments were executed on a computer with 4-core CPU, 8 GiB RAM and Ubuntu 18.4-LVM OS. The timeout was set to 10s for each test. The summary of experimenting for each benchmark group is given in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively. Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulae. Columns with heading \texttt{timeout} indicate the number of times the solver exceeded the time limit and columns with heading $\times$ show numbers of instances for which the particular solver either reported unknown or reported invalid answer or crashed.

\hide{
In this section, we compare our implementation z3-Trau with other SMT tools cvc4, z3, and z3-str3 as evauation. To show the general performance of z3-Trau, we compare z3-Trau with other string solvers on selected string benchmarks: PyEx is a benchmark obtained from symbolic execution of Python code[]; APLAS is a benchmark involving looping word equations[]; 
LeetCode is obtiained from concolic testing LeetCode solutions written in Python code; StringFuzz is a benchmark of instance SMT-lib string problems generated by StringFuzz generator tool[]; cvc4\textsubscript{pred} and cvc4\textsubscript{term} are benchmarks provided by the cvc4 development team[]. Table~\ref{table:base_benchmark} shows the result of the comparison. The experiments are conducted with machines of the following specifications: 4-core CPU, 8GB RAM, Ubuntu 18.4-LVM OS. We set the timeout is to 10 seconds. Because the amount of problems is very large, we ran these experiments separately on several machines with the same specification on a computer cluster. The results are either sat, unsat, timeout, or $\times$. In case $\times$, the result may be unknown, error, or exception.
}
